Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs with the Uniform Kernel

### 2016-02-29 main_paper.tex
Make minor edits to the abstract

\begin{abstract}\noindent
  This paper develops a novel bootstrap procedure to obtain robust
  bias-corrected confidence intervals in regression discontinuity designs that
  use the uniform kernel. The procedure uses a residual bootstrap to estimate
  the bias of the RD estimator, which is then removed from the original estimator.
 The bias-corrected estimator is then bootstrapped itself to
  generate valid confidence intervals. This procedure is valid for empirically
  relevant bandwidths when the residual bootstraps use a polynomial of higher
  order than used to estimate the treatment effect and can be applied under the
  same conditions as Calonico, Cattaneo and Titiunik's (2014,
  \textit{Econometrica}) analytical correction.
\end{abstract}

>>>>

\begin{abstract}\noindent
  This paper develops a novel bootstrap procedure to obtain robust
  bias-corrected confidence intervals in regression discontinuity designs that
  use the uniform kernel. The procedure uses a residual bootstrap to estimate
  the bias of the RD estimator, which is then removed from the original
  estimator.  The bias-corrected estimator is then bootstrapped itself to
  generate valid confidence intervals. This procedure is valid for empirically
  relevant bandwidths when the treatment effect is estimated with a local linear
  model and the residual bootstraps use a second order polynomial; validity
  holds under similar conditions to Calonico, Cattaneo and Titiunik's (2014,
  \textit{Econometrica}) analytical correction.
\end{abstract}
